\chapter*{Abstract (Magdalena Solecka)}
\par The subject of the following engineering diploma thesis was travel planning 
platform with mobile client application. In order to develop the project, public 
databases that contained necessary information related to tourist attractions and 
transport posibilities between two locations were used. A storage option for important 
documents and a recommendation mechanism for travel plan elements were implemented. 
A possiblity of sharing travel with other application users and publishing its element 
in social media was also included.
 
\par Chapter 1 introduces the subject of this diploma thesis and justifies the purposes 
of producing this mobile application. 
 
\par Chapter 2 contains overview of similar solutions with essential advantages and 
disadvanteges identification.

\par Chapter 3 points out the most important requirements and goals with an extract from 
system requirements specification document.

\par Chapter 4 includes system architecure design that consists of component diagram of 
the server side as well as the client application. It also contains usage scenario 
examples.

\par Chapter 5 justifies fundamental project decisions such as: programming language, 
programming tools and version control system choice.

\par Chapter 6 describes design pattern followed during mobile app implementation. It 
also includes description of implementation of specific features as well as resolving 
communication problems with server application.

\par Chapter 7 contains server side implementation, database and external API connection 
were considered. It also explains places recommendation process. 

\par Chapter 8 includes a description of working process with chosen database and entity 
relationship diagram.

\par Chapter 9 refers to different types of tests performed with examples.

\par Chapter 10 contains the most important features. It includes guidelines for 
application user with screenshots.

\par Chapter 11 is a summary of the entire project.

\par \textbf{Tasks division} (more specific in extra A):
\begin{itemize}
\item Anna Malizjusz -- plan and implementation server basic form, communication with 
external API and implemention of search objects feature,
\item Dorota Tomczak -- plan and implementation client application basic form, 
recommendation mechanism and documents scanning,
\item Magdalena Solecka -- plan and implementation of database basic form, add travel 
mechanism and delete mode implementation,
\item Karolina Makuch -- search and adding user to friends list, share travel 
mechanisms, manual plan realization.
\end{itemize}
\textbf{Keywords}: mobile application, travel, planning